LSST Alerts: A Menu of Options

### 2019-11-15 dmtn-tbd.tex
added draft state warning

\setDocAbstract{%
A review and discussion of the variety of options for alert packets and their distribution, such as latency timescale, packet contents, pre-stream filtering, and so forth.
}

>>>>

\setDocAbstract{%
\textcolor{red}{\bf EXTREME DRAFT STATE. DO NOT READ. DO NOT CITE.}\\
A review and discussion of the variety of options for alert packets and their distribution, such as latency timescale, packet contents, pre-stream filtering, and so forth.
}
